Field work 2016

### 2017-03-01 analysis/spatial_focal_tree.Rmd
change point apparence

```{r pacakges}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")
library("tidyverse")
```

```{r readData}
mymachine <- '/Users/ajpeluLap/' 
# mymachine <- '/Users/ajpelu/' 
di <- paste0(mymachine, 'Dropbox/phd/phd_repos/qpyr_dendro/')

@@

ots_phe <- ots[ots$notes == 'Fenologia_Obsnev',]
ots_gea <- ots[ots$notes == 'GeaIzquierdo2014',]

```{r}
mymap <- leaflet() %>% 
  # BaseMaps 
  addWMSTiles('http://www.ideandalucia.es/wms/ortofoto2009?',
              layers = 'oca10_2008-09',
              options = WMSTileOptions(format = "image/png", transparent = FALSE),
              attribution = '<a href="http://www.juntadeandalucia.es/institutodeestadisticaycartografia" target="_blank">Instituto de Estadística y Cartografía de Andalucía</a>',
              group = 'Ortophotography 2009') %>%
   addWMSTiles('http://www.ideandalucia.es/services/toporaster10/wms?',
              layers = 'toporaster10',
              options = WMSTileOptions(format = "image/png", transparent = FALSE),
              attribution = '<a href="http://www.juntadeandalucia.es/institutodeestadisticaycartografia" target="_blank">Instituto de Estadística y Cartografía de Andalucía</a>',
              group = 'Topographical') %>%

  # Layers control
  addLayersControl(position = 'bottomright',
                   # baseGroups = c("Topographical","Ortophotography 2009","PNOA"),
                   baseGroups = c("Ortophotography 2009", "Topographical"),
                   overlayGroups = c("Field Work 2016", "Migrame", "OBSNEV Fen", "Gea Izquierdo 2014"),
                   options = layersControlOptions(collapsed = FALSE))
```

```{r}
myext <- extent(mig_forest_sj)

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_sj, color='blue', group='Migrame', popup=mig_forest_sj$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name) %>% 
   addCircles(my_points, 
             lng=coordinates(my_points)[,'coords.x1'], 
             lat=coordinates(my_points)[,'coords.x2'], 
             group='Field Work rep ', radius=2, color = 'purple', popup=my_points$name)

```{r}
myext <- extent(mig_forest_ca)

>>>>

```{r pacakges, warning=FALSE, message=FALSE}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")
library("tidyverse")
```

```{r readData}
# mymachine <- '/Users/ajpeluLap/' 
mymachine <- '/Users/ajpelu/' 
di <- paste0(mymachine, 'Dropbox/phd/phd_repos/qpyr_dendro/')

# Read spatial data 
# Centroid of focal tree 
## filename 
mygpx_ca <- paste0(di, 'data_raw/geoinfo/dendro_ca.GPX')
mygpx_sj <- paste0(di, 'data_raw/geoinfo/dendro_sj.GPX')

## reading  
field_work_ca <- readOGR(mygpx_ca, layer="waypoints", verbose = FALSE)
field_work_sj <- readOGR(mygpx_sj, layer="waypoints", verbose = FALSE)
```

```{r prepareBaseMap}
nombre_capas_base <- c("Ortophotography 2009", "Topographical")
nombre_capas_overlay <- c("Field Work 2016")

mymap <- leaflet() %>% 
  # BaseMaps 
  addWMSTiles('http://www.ideandalucia.es/wms/ortofoto2009?',
              layers = 'oca10_2008-09',
              options = WMSTileOptions(format = "image/png", transparent = FALSE),
              attribution = '<a href="http://www.juntadeandalucia.es/institutodeestadisticaycartografia" target="_blank">Instituto de Estadística y Cartografía de Andalucía</a>',
              group = 'Ortophotography 2009') %>%
   addWMSTiles('http://www.ideandalucia.es/services/toporaster10/wms?',
              layers = 'toporaster10',
              options = WMSTileOptions(format = "image/png", transparent = FALSE),
              attribution = '<a href="http://www.juntadeandalucia.es/institutodeestadisticaycartografia" target="_blank">Instituto de Estadística y Cartografía de Andalucía</a>',
              group = 'Topographical') %>%

  # Layers control
  addLayersControl(position = 'bottomright',
                   baseGroups = nombre_capas_base,
                   overlayGroups = nombre_capas_overlay,
                   options = layersControlOptions(collapsed = FALSE))
```

```{r}
# Spatial object 
fw <- field_work_sj

# Set spatial extension 
myext <- extent(fw)

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=5, 
             color = 'red', popup=fw$name, 
             stroke = TRUE, fillOpacity = 0.5)

```{r}
# Spatial object 
fw <- field_work_ca

# Set spatial extension 
myext <- extent(fw)

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=5, 
             color = 'red', popup=fw$name, 
             stroke = TRUE, fillOpacity = 0.5)

```{r eval=FALSE, echo=FALSE}

@@

ots_phe <- ots[ots$notes == 'Fenologia_Obsnev',]
ots_gea <- ots[ots$notes == 'GeaIzquierdo2014',]
myext <- extent(mig_forest_ca)
